---
title: "HW8"
author: "Ethan Dean"
date: "March 31 2021"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

# Study System

I am using the example data from an experiment I am creating on CPB. In this I am exposing beetles to curcumin and seeing how that changes their survival because it should cause changes in their epigenetic mechanisms possibly associated with insecticide resistance.

If this were true I would see less survive when exposed to the determined LC50 when exposed to these chemicals.

# Deciding on Data formats

I decided on the values based on my previous research into the topic and talking with the other people in my lab. Generally this is the ideal outcome I would like with a 25% increase in mortality, however when looking at the minimum needed value (helping me determine variance) they said that in my experiment a change of a few percent would still generally be significant.

I also did this many beetles because I cannot do this in lab because of time being an undergraduate, but ideally I would love 1000 replicates.

# Creating Random Data and Analyze the data

___

```{r}
library(ggplot2)

# Control survival when exposed to lc50 with survivors being 1

Survival_C = rnorm(1000, mean = 0.5, sd = 1)

# 0.25mg curcumin exposure survival rate

Survival_L = rnorm(1000, mean = 0.4, sd = 1)

# 1mg curcumin exposure survival rate

Survival_H = rnorm(1000, mean = 0.3, sd = 1)

# Organize data ------------------------------

survival_total = data.frame(ID = 1:3000, c(Survival_C, Survival_L, Survival_H), Treatment = c(rep('control', 1000), rep('low_curcumin', 1000), rep('high_curcumin', 1000)))

colnames(survival_total)[2] <- ('Survival')

# analyze the data ------------------------------

summary_surv = summary(survival_total)
print(summary_surv)

stats <- aov(Survival ~ Treatment, data = survival_total)

stats_sum <- summary(stats)

print(stats_sum)

# create a boxplot ------------------------------

ano_plot <- ggplot(stats) + aes(x = Treatment, y = Survival) + geom_boxplot()

print(ano_plot)
```

# Running an additional time

___

```{r}
library(ggplot2)

# create data ------------------------------

# Control survival when exposed to lc50 with survivors being 1

Survival_C = rnorm(1000, mean = 0.5, sd = 1)

# 0.25mg curcumin exposure survival rate

Survival_L = rnorm(1000, mean = 0.4, sd = 1)

# 1mg curcumin exposure survival rate

Survival_H = rnorm(1000, mean = 0.3, sd = 1)

# Organize data ------------------------------

survival_total = data.frame(ID = 1:3000, c(Survival_C, Survival_L, Survival_H), Treatment = c(rep('control', 1000), rep('low_curcumin', 1000), rep('high_curcumin', 1000)))

colnames(survival_total)[2] <- ('Survival')

# analyze the data ------------------------------

summary_surv = summary(survival_total)
print(summary_surv)

stats <- aov(Survival ~ Treatment, data = survival_total)

stats_sum <- summary(stats)

print(stats_sum)

# create a boxplot ------------------------------

ano_plot <- ggplot(stats) + aes(x = Treatment, y = Survival) + geom_boxplot()

print(ano_plot)
```

# Adjusted Means

The closest I could get was within 4 percent and still get significance. This is actually the perfect percentage that I was hoping to get in the experiments that I am running.

___

```{r}
library(ggplot2)

# create data ------------------------------

# Control survival when exposed to lc50 with survivors being 1

Survival_C = rnorm(1000, mean = 0.5, sd = 1)

# 0.25mg curcumin exposure survival rate

Survival_L = rnorm(1000, mean = 0.46, sd = 1)

# 1mg curcumin exposure survival rate

Survival_H = rnorm(1000, mean = 0.43, sd = 1)

# Organize data ------------------------------

survival_total = data.frame(ID = 1:3000, c(Survival_C, Survival_L, Survival_H), Treatment = c(rep('control', 1000), rep('low_curcumin', 1000), rep('high_curcumin', 1000)))

colnames(survival_total)[2] <- ('Survival')

# analyze the data ------------------------------

summary_surv = summary(survival_total)
print(summary_surv)

stats <- aov(Survival ~ Treatment, data = survival_total)

stats_sum <- summary(stats)

print(stats_sum)

# create a boxplot ------------------------------

ano_plot <- ggplot(stats) + aes(x = Treatment, y = Survival) + geom_boxplot()

print(ano_plot)

```

# Minimum Sample

The lowest I could get here was 360. Even changing a little bit to 350 it seemed made all of the data insignificant. This was good as the sample was cut down close to a third and still showed significance.

___

```{r}

# create data ------------------------------

# Control survival when exposed to lc50 with survivors being 1

Survival_C = rnorm(360, mean = 0.5, sd = 1)

# 0.25mg curcumin exposure survival rate

Survival_L = rnorm(360, mean = 0.4, sd = 1)

# 1mg curcumin exposure survival rate

Survival_H = rnorm(360, mean = 0.3, sd = 1)

# Organize data ------------------------------

survival_total = data.frame(ID = 1:360, c(Survival_C, Survival_L, Survival_H), Treatment = c(rep('control', 360), rep('low_curcumin', 360), rep('high_curcumin', 360)))

colnames(survival_total)[2] <- ('Survival')

# analyze the data ------------------------------

summary_surv = summary(survival_total)
print(summary_surv)

stats <- aov(Survival ~ Treatment, data = survival_total)

stats_sum <- summary(stats)

print(stats_sum)

# create a boxplot ------------------------------

ano_plot <- ggplot(stats) + aes(x = Treatment, y = Survival) + geom_boxplot()

print(ano_plot)
```