---
title: "HW9"
author: "Ethan Dean"
date: "April 07 2021"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

# Question 1
This is basically the same output as my other, except I changed the distribution to be a gamma as opposed to a normal distribution to be more realistic to the data that I would collect in real life. While I needed to have normal in the last homework, gamma is more realistic for a survivability when the numbers are low to avoid a negative survivability rating.

```{r}
# -----------------------------------
# A script that moves the information from HW8 into structured programming
# 07 Apr 2021
# EMD
# -----------------------------------
#

# Import libraries ------------------------------

library(ggplot2)


# -----------------------------------
# FUNCTION create_data
# description: this function creates data if there is no data input
# inputs: a null variable that will be then manipulated
# outputs: the output of this function should be three strings of data for separate trials
#####################################
create_data <- function(x=NULL) {
  if (is.null(x)) {
    Survival_C = rgamma(1000, shape = 0.5, scale = 0.1)
    Survival_L = rgamma(1000, shape = 0.35, scale = 0.1)
    Survival_H = rgamma(1000, shape = 0.25, scale = 0.1)
  }

  d8ta <- c(Survival_C, Survival_L, Survival_H)
return(d8ta)
  
} # end of create_data
# -----------------------------------





# -----------------------------------
# FUNCTION org_data
# description: This function orders the data that was created from the create data function
# inputs: The input will be one list of strings
# outputs: the output will be a data frame
#####################################
org_data <- function(A = c(Survival_C = runif(1000), Survical_L = runif(1000), Survival_H = runif(1000))) {
  
  Survival_C <- A[1:1000]
  Survival_L <- A[1001:2000]
  Survival_H <- A[2001:3000]
  
  survival_total = data.frame(ID = 1:3000, c(Survival_C, Survival_L, Survival_H), Treatment = c(rep('control', 1000), rep('low_curcumin', 1000), rep('high_curcumin', 1000)))
  
  colnames(survival_total)[2] <- ('Survival')


return(survival_total)

} # end of org_data
# -----------------------------------





# -----------------------------------
# FUNCTION data_analyze
# description: this take the data and gets the summery stats
# inputs: a dataframe df
# outputs: outputs summary stats
#####################################
data_analyze <- function(x) {

  summary_surv = summary(x)
  print(summary_surv)
  
  stats <- aov(Survival ~ Treatment, data = x)
  
  stats_sum <- summary(stats)

  
return(stats_sum)

} # end of data_analyze
# -----------------------------------





# -----------------------------------
# FUNCTION box_plot
# description: creates a box plot of the analyzed data
# inputs: stats of an AOV of the data   
# outputs: a box plot
#####################################
box_plot <- function(orged_data) {
  
  ano_plot <- ggplot(orged_data) + aes(x = Treatment, y = Survival) + geom_boxplot()
  
  

return(ano_plot)

} # end of box_plot
# -----------------------------------





# -----------------------------------
# FUNCTION data_compile
# description: this function uses other functions to import data from another file, analyze it and then output a graph plot of the data
# inputs: data
# outputs: the outputs of this are summary stats as well as a boxplot of the data
#####################################
data_compile <- function(x=NULL) {
  if (is.null(x)) {
    x <- create_data()
  }
  data_organized <- org_data(x)
  stats <- data_analyze(data_organized)
  plotted<- box_plot(data_organized)
  
  print(stats)
  print(plotted)
return()

} # end of function_name
# -----------------------------------

data_compile()

```

# Question 2
Here I changed up my graph to output a different type of display which might be useful for seeing the distribution of survivability. This is cool because here you can see the shifting to the left of the trials as there is more curcumin in the diet of the beetles. 

```{r}
# -----------------------------------
# A script that moves the information from HW8 into structured programming
# 07 Apr 2021
# EMD
# -----------------------------------
#

# Import libraries ------------------------------

library(ggplot2)


# -----------------------------------
# FUNCTION create_data
# description: this function creates data if there is no data input
# inputs: a null variable that will be then manipulated
# outputs: the output of this function should be three strings of data for separate trials
#####################################
create_data <- function(x=NULL) {
  if (is.null(x)) {
    Survival_C = rgamma(1000, shape = 0.5, scale = 0.1)
    Survival_L = rgamma(1000, shape = 0.35, scale = 0.1)
    Survival_H = rgamma(1000, shape = 0.25, scale = 0.1)
  }

  d8ta <- c(Survival_C, Survival_L, Survival_H)
return(d8ta)
  
} # end of create_data
# -----------------------------------





# -----------------------------------
# FUNCTION org_data
# description: This function orders the data that was created from the create data function
# inputs: The input will be one list of strings
# outputs: the output will be a data frame
#####################################
org_data <- function(A = c(Survival_C = runif(1000), Survical_L = runif(1000), Survival_H = runif(1000))) {
  
  Survival_C <- A[1:1000]
  Survival_L <- A[1001:2000]
  Survival_H <- A[2001:3000]
  
  survival_total = data.frame(ID = 1:3000, c(Survival_C, Survival_L, Survival_H), Treatment = c(rep('control', 1000), rep('low_curcumin', 1000), rep('high_curcumin', 1000)))
  
  colnames(survival_total)[2] <- ('Survival')


return(survival_total)

} # end of org_data
# -----------------------------------





# -----------------------------------
# FUNCTION data_analyze
# description: this take the data and gets the summery stats
# inputs: a dataframe df
# outputs: outputs summary stats
#####################################
data_analyze <- function(x) {

  summary_surv = summary(x)
  print(summary_surv)
  
  stats <- aov(Survival ~ Treatment, data = x)
  
  stats_sum <- summary(stats)

  
return(stats_sum)

} # end of data_analyze
# -----------------------------------





# -----------------------------------
# FUNCTION box_plot
# description: creates a box plot of the analyzed data
# inputs: stats of an AOV of the data   
# outputs: a box plot
#####################################
density_plot <- function(orged_data) {
  
  ano_plot <- ggplot(orged_data) + aes(x = Survival, fill = Treatment) + geom_density(alpha = 0.8)
  
  

return(ano_plot)

} # end of box_plot
# -----------------------------------





# -----------------------------------
# FUNCTION data_compile
# description: this function uses other functions to import data from another file, analyze it and then output a graph plot of the data
# inputs: data
# outputs: the outputs of this are summary stats as well as a boxplot of the data
#####################################
data_compile <- function(x=NULL) {
  if (is.null(x)) {
    x <- create_data()
  }
  data_organized <- org_data(x)
  stats <- data_analyze(data_organized)
  plotted<- density_plot(data_organized)
  
  print(stats)
  print(plotted)
return()

} # end of function_name
# -----------------------------------

data_compile()

```